---
title: | 
       | Introduction to the AUTtheme 
       | for R Markdown with Beamer
       
author: "Sarah Marshall"
institute: |
           | Department of Mathematical Sciences
           | Auckland University of Technology
date: |
      | 24 February 2023
output: 
  beamer_presentation: 
    latex_engine: lualatex
    slide_level: 3
    includes:
      in_header: header.tex
    keep_tex: yes
classoption: "aspectratio=169"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Overview
\tableofcontents[hideallsubsections]

# Usage


## How to load this package

Load this package from github using the `remotes` package

```{r, eval=FALSE}
#install.packages("remotes") 
remotes::install_github("sarahemarshall/aut-theme")
```

In R Studio

-   File/New File/R Markdown/From Template
-   Select AUTBeamer

This will create a new directory containing the required files to run
the template

-   bgImages (folder containing images)
-   AUTtheme.sty
-   header.tex
-   untitled.Rmd

## Compiling this demo file

To compile this demo file, this file needs to be located in the same
directory as the `bgImages` folder and the `AUTtheme.sty` file. These files 
are not provided in the demo folder to avoid duplication.

## Compiling with AUTTheme

`lualatex` is recommended.


## Comparison to Beamer version

The Rmd version of this template does not yet have all the functionality
of the beamer version, e.g. customised frame environments such as sectionpages.

# Frames

## Frame Sizes

The template can be used to create $16\times9$ or $4 \times 3$ slides
 by modifying the YAML header.
 
The resolution of the background images get updated automatically.

-   To create $16 \times 9$ slides use
    `classoption: "aspectratio=169"`
-   To create $4 \times 3$ slides use
    `classoption: "aspectratio=43"`

## Customisation

The file `header.tex` contains the LaTeX commands used at the start of
the document.

To use the AUTtheme package, `header.tex` needs to contain, a command
like: 

* `\usepackage{AUTtheme}` or 
* `\usepackage[dct]{AUTtheme}`

The `header.tex` file can also be used to load other packages or
customise the Beamer package in other ways, e.g.

`\AtBeginSection{}`

or

`usepackage{lipsum}`


## Outlines

Sections are defined by `#`, subsections by `##` and slides by `###`.
The `slide_level` can be defined in the YAML header.

An outline of all sections can be created by adding:

`\tableofcontents[hideallsubsections]`




### Overview - Example 1 {.unnumbered}

\tableofcontents[hideallsubsections]


### Overview - Example 2 {.unnumbered}

\tableofcontents[
    	currentsection,
      sectionstyle=show/shaded,
      subsectionstyle = hide/hide/hide
    ]
    
    
### Overview - Example 3 {.unnumbered}

\tableofcontents[
    	currentsection,
      sectionstyle=show/shaded,
      subsectionstyle=show/shaded/hide
    ]
        
     
        

## `\AtBeginSection`

In `AUTtheme.sty` the default is that each section starts:

*  with a title slide containing the section name
*  an outline slide with the following specification

```{r, echo = TRUE, eval = FALSE}
\tableofcontents[
      currentsubsection,
      sectionstyle=show/shaded,
      subsectionstyle=show/shaded/hide,
    ]
```


## Customising `\AtBeginSection`
This can be customised in `header.tex`.  For example, as shown in the header file for this demo 

```{r, echo = TRUE, eval = FALSE}
\AtBeginSection{
\begin{sectionframe}
\frametitle{Outline}
\tableofcontents[
    	currentsection,
        sectionstyle=show/shaded,
        subsectionstyle=show/show/hide,
    ]
\end{sectionframe}}
```



# Common Frame Features and Layouts

## Lists

### Unordered list

-   Bullet 1
    -   sub Bullet
        -   sub of sub Bullet
    -   sub Bullet
-   Bullet 2
-   Bullet 3

### Ordered list

1.  Item 1
    -   Item 1a
    -   Item 1b
2.  Item 2
3.  Item 3
    -   Item 3a
    -   Item 3b

### List with steps showing

> 1.  Item 1
> 2.  Item 2
> 3.  Item 3



## Columns 

:::  {.columns align=top}

::::  {.column width="60%"}
Column 1

```{r, echo=FALSE, out.width="100%"}
plot(1:10, 1:10)
```

::::

::::  {.column width="40%"}
```{r, echo=FALSE, out.width="100%"}
plot(1:10, 1:10)
```
Column 2
::::

:::

## Tables

|            |           |          |         |
|------------|-----------|----------|---------|
| Assessment | Weighting | Hand out | Hand in |
| Quizzes    | 15%       | Weekly   | Weekly  |
| Assignment | 25%       | Week 6   | Week 8  |
| Project    | 60%       | Week 4   | Week 12 |
| Total      | 100%      |          |         |


# LaTeX commands


## Overlays

This appears on all slides. 
\only<2->{ \textbf{This only appears on slide 2}
}

## Footnotes

There is a really good book about geometric processes.
\footnote[frame]{
Lam, Yeh. The Geometric Process and Its Applications. World Scientific, Hackensack,
NJ, 2007.
}
There is also a really good book about stochastic processes.
\footnote[frame]{
Ross, Sheldon. Stochastic Processes, 1998.
}

## Protecting LaTeX commands

The following environment can be used to protect raw latex code (see source)
```{=latex}
\begin{tabular}{ll}
A & B \\
A & B \\
\end{tabular}
```

## LaTeX Environments

### Example 1

For more information see <https://bookdown.org/yihui/rmarkdown-cookbook/custom-blocks.html>

 

:::: {.center data-latex=""}

::: {.minipage data-latex="{.5\linewidth}"}
This paragraph will be centered on the page, and
its width is 50% of the width of its parent element.
:::

::::





