---
title: | 
       | Introduction to the AUTtheme 
       | for R Markdown with Beamer
       
author: "Sarah Marshall"
institute: |
           | Department of Mathematical Sciences
           | Auckland University of Technology
date: |
      | 24 February 2023
output: 
  beamer_presentation:
    keep_tex: false
    latex_engine: lualatex    
    slide_level: 3
    includes:
      in_header: header.tex
classoption: "aspectratio=169"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Usage

### How to load this package

Load this package from github using the `remotes` package

```{r, eval=FALSE}
#install.packages("remotes") 
remotes::install_github("sarahemarshall/aut-theme")
```

In R Studio

-   File/New File/R Markdown/From Template
-   Select AUTBeamer

This will create a new directory containing the required files to run
the template

-   bgImages (folder containing images)
-   AUTtheme.sty
-   header.tex
-   untitled.Rmd

## Compiling this demo file

To compile this demo file, this file needs to be located in the same
directory as the `bgImages` folder and the `AUTtheme.sty` file. These files 
are not provided in the demo folder to avoid duplication.


## Frames

### Frame Sizes

The template can be used to create $16\times9$ or $4 \times 3$ slides
 by modifying the YAML header.
 
The resolution of the background images get updated automatically.

-   To create $16 \times 9$ slides use
    `classoption: "aspectratio=169"`
-   To create $4 \times 3$ slides use
    `classoption: "aspectratio=43"`

### Customisation

The file `header.tex` contains the LaTeX commands used at the start of
the document.

To use the AUTtheme package, `header.tex` needs to contain, a command
like: 

* `\usepackage{AUTtheme}` or 
* `\usepackage[dct]{AUTtheme}`

The `header.tex` file can also be used to load other packages or
customise the Beamer package in other ways, e.g.

`\AtBeginSection{}`

or

`usepackage{lipsum}`

### Compiling with AUTTheme

`lualatex` is recommended.


## Comparison to Beamer version

The Rmd version of this template does not yet have all the functionality
of the beamer version, e.g. customised frame environments such as sectionpages.

## Lists

### Unordered list

-   Bullet 1
    -   sub Bullet
        -   sub of sub Bullet
    -   sub Bullet
-   Bullet 2
-   Bullet 3

### Ordered list

1.  Item 1
    -   Item 1a
    -   Item 1b
2.  Item 2
3.  Item 3
    -   Item 3a
    -   Item 3b

### List with steps showing

> 1.  Item 1
> 2.  Item 2\
> 3.  Item 3
